\section{Hardware Description}
\label{sec:hardware}
We use AWS Cloud Instance~\cite{awsi4} for our project and experiments. The basic hardware configuration for our instance is as follows.

\paragraph{Processor.} The table below shows the processor description.
\begin{table}[h]
	\centering
	\begin{tabular}{c|c}
		\hline
		CPU Model & Intel Xeon Platinum 8259CL  \\ \hline
		
		CPU(s) & 2 vCPUs \\ \hline

		CPU MHz & 2.50GHz \\ \hline
		
		L1 data cache & 32 KiB \\ \hline
		L1 instruction cache & 32 KiB \\ \hline
		L2 cache & 1 MiB \\ \hline
		L3 cache & 35.8 MiB \\ \hline
		Architecture & x86\_64 \\ \hline
	\end{tabular}
	\caption{\textbf{Processor Description}}
	\label{table:sys-conf}
	%\vspace{-7mm}
\end{table}

\paragraph{Memory bus.} In our AWS Instance, we have a Physical Memory Array (PMA) in memory bus. The detailed configuration of the PMA is as follows:
\begin{itemize}[leftmargin=*]
	\item Location: System Board Or Motherboard
	\item Use: System Memory
	\item Error Correction Type: Unknown
	\item Maximum Capacity: 904 MiB
	\item Error Information Handle: Not Provided
	\item Number of Devices: 1
\end{itemize}

\paragraph{I/O bus.} The following shows the detailed I/O bus configuration about our AWS Instance.
\begin{itemize}[leftmargin=*]
	\item Host bridge: Intel Corporation 440FX - 82441FX PMC
	\item ISA bridge: Intel Corporation 82371SB PIIX3 ISA 
	\item Non-VGA unclassified device: Intel Corporation
	\item VGA compatible controller: Amazon.com, Inc.
	\item Non-Volatile memory controller: Amazon.com, Inc. NVMe EBS Controller
	\item Ethernet controller: Amazon.com, Inc. Elastic Network Adapter (ENA)
\end{itemize}

\paragraph{Others.} The other hardware description is shown as follows:
\begin{table}[h]
	\centering
	\begin{tabular}{c|c}
		\hline
		Memory & 904MiB DDR4 DRAM \\ \hline
		
		Storage & NVMe SSD 8GB without cache \\ \hline

		Network & 28Gbps \\ \hline
		
		OS & Amazon Linux version 2022, release 2022 \\ \hline
	\end{tabular}
	\caption{\textbf{Experimental System Configuration.}}
	\label{table:sys-conf}
	%\vspace{-7mm}
\end{table}


