\section{Introduction}
\label{sec:intro}
In this project, our goal is to help other students to deeply understand computer systems including concepts and its associated behaviors. To achieve this goal, our group members, Yanbo Zhou and Xiaochuan Yu, will build specific measurement tools and conduct experiments on system-level. Furthermore, we will analyze our experimental results based on the computer system concepts.

Our measurement and experiments are conducted on AWS EC2 Instance. Note that since we use EC2 Instance that is a virtualized environment, the virtualization layer will introduce part of overhead for our experiments. Therefore, the results may include the Guest Operating System (OS) operations and underlying virtualization overhead. In this report, we focus on methodology on measuring computer system. You can also use the methodology and our provided tools on physical machines, in order to avoid the virtualization overhead on EC2 Instance.

In the rest of this report, we will first introduce our hardware description in Section~{\S\ref{sec:hardware}}. Then we talk about CPU, Scheduling, and OS Services in Section~{\S\ref{sec:cpu}}; Memory in Section~{\S\ref{sec:memory}}; Network in Section~{\S\ref{sec:network}}; and File System in Section~{\S\ref{sec:file}}. Finally, we summarize our experiments and report in Section~{\S\ref{sec:summary}}. Xiaochuan Yu is responsible for CPU, Scheduling, OS Service, and Network experiments, and Yanbo Zhou will be responsible for Memory and File System experiments.
